Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-13 providence/sections/intro.tex
Update intro.tex

\subsection{Our Contributions}
Our primary contribution is a new RLA, \Providence, which gives the efficiency of \Minerva and is also resistant to a strong adversary. Additionally, \Providence does not assume that the null hypothesis is a tied election and hence is more broadly useful than \Minerva. \BRAVO is a very flexible audit enabling audit planning; with the introduction of \Providence, similar planning is possible with greater efficiency. In a contest with a narrow margin (in the 2020 US Presidential election, eight states had margins smaller than 0:03) the difference in number of ballots sampled using \Providence over \BRAVO could correspond to many days of work which would need to be completed before a certification deadline.

The stopping condition for \Minerva does not take into account the sample obtained in previous rounds, and, in \cite{usenix_minerva}, its risk limit is estimated through weighted averages across multiple rounds, assuming that round sizes do not depend on the previous sample. Further, it assumes that the null hypothesis is a tie. A far simpler proof is possible for the risk-limiting property of \Providence. In particular, the proof does not require an assumption about round sizes and does not assume any particular fractional vote distribution for the null.

@@

\Providence may be used in any audit, stratified or otherwise, where audited contests may be expressed as pairwise plurality contests: for example, it can be used in plurality and majoritarian elections.

>>>>

\subsection{Our Contributions}
Our primary contribution is a new RLA, \Providence, which gives the efficiency of \Minerva and is also resistant to a strong adversary. 
%Additionally, \Providence does not assume that the null hypothesis is a tied election and hence is more broadly useful than \Minerva. 
\BRAVO is a very flexible audit enabling audit planning; with the introduction of \Providence, similar planning is possible with greater efficiency. In a contest with a narrow margin (in the 2020 US Presidential election, eight states had margins smaller than 0:03) the difference in number of ballots sampled using \Providence over \BRAVO could correspond to many days of work which would need to be completed before a certification deadline.

The stopping condition for \Minerva does not take into account the sample obtained in previous rounds, and, in \cite{usenix_minerva}, its risk limit is estimated through weighted averages across multiple rounds, assuming that round sizes do not depend on the previous sample. 
%Further, it assumes that the null hypothesis is a tie. A far simpler proof is possible for the risk-limiting property of \Providence. 
In particular, the proof does not require an assumption about round sizes.

@@

\Providence may be used in any audit where audited contests may be expressed as pairwise plurality contests: for example, it can be used in plurality and majoritarian elections.
